New lower bounds for Schur and weak Schur numbers

### 2021-04-18 article/schur.tex
modif conclusion partie schur

\begin{corollary}
The growth rate for Schur numbers (and Ramsey numbers \(R_n(3)\))  satisfies \(\gamma \geqslant \sqrt[5]{380} \approx 3.28 \).
\end{corollary}

@@

>>>>

\begin{corollary}
The growth rate for Schur numbers (and Ramsey numbers \(R_n(3)\))  satisfies \(\gamma \geqslant \sqrt[5]{380} \approx 3.28\).
\end{corollary}

@@

\qquad In this section, we first formalized Rowley's template-based constructions \cite{RowleyRamsey} in the context of Schur numbers 
by introducing SF-templates as well as a new sequence, \(S^+\). We provided relations between \(S^+\) and \(S\) then 
stated Rowley's construction method in the context of Schur numbers. We found new SF-templates allowing us to obtain 
new lower bounds for schur numbers. One may notice that we mostly gave only lower bounds for \(S^+\). It should be possible to 
find better SF-templates by making different assumptions or using a different method (Monte-Carlo methods for instance).

\par
In the next section, we provide similar results for weak Schur numbers. We introduce WSF-templates and a corresponding sequence, 
\(WS^+\). We then derive similar relations and construction method allowing us to find new lower bounds for weak Schur numbers.
